---
title: "HW 7"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE,  
                      warning = FALSE, message = FALSE, 
                      fig.align = "center",
                      R.options = list(max.print=100))

# Edit the file starting below
```

### Enter your name and EID here:

**You will submit this homework assignment as a pdf file on Gradescope.**

*For all questions, include the R commands/functions that you used to find your answer (show R chunk). Answers without supporting code will not receive credit. Write full sentences to describe your findings.*

We will use the packages `tidyverse` and  `plotROC` for this assignment. If you do not have the `plotROC` package (i.e. loading the package with `library()` produces an error), then you should install it separately before doing this assignment.

```{r, message = FALSE}
# Load packages
library(tidyverse)
library(plotROC)
```

------------------------------------------------------------------------

## Question 1: (4 pts)

We will use the `pokemon` dataset for this assignment:

```{r}
# Upload data from GitHub
pokemon <- read_csv("https://raw.githubusercontent.com/laylaguyot/datasets/main//pokemon.csv")

# Take a look 
head(pokemon)
```

Recode the variable `Legendary`, taking a value of 0 if a pokemon is not legendary and a value of 1 if it is. Save the resulting data as `my_pokemon`.

```{r}
# your code goes below (make sure to edit comment)
 
```

Visualize the linear relationship between `Attack` and `HP` (hit points) for each legendary status. 

*Hint: For the plot, convert the legendary status binary variable to a factor using `as.factor()`.* 

Do `Attack` and `HP` seem to predict Legendary status? Comment with what you see in the visualization.

```{r}
# your code goes below (make sure to edit comment)
 
```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 2: (2 pt)

Let's predict `Legendary` status using a linear regression model with `Attack` and `HP` in `my_pokemon`. Fit this model, call it `pokemon_lin`, and write its equation.

```{r}
# your code goes below (make sure to edit comment)
 
```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 3: (3 pts)

Choose a pokemon whose name starts with the same letter as yours. Take a look at its stats and, using the equation of your model from the previous question, predict the legendary status of this pokemon, "by hand" (multiplying the predictors with the estimated coefficients):

```{r}
# your code goes below (make sure to edit comment)
 
```

Check your answer by using `predict()` with the argument `newdata =`:

```{r}
# your code goes below (make sure to edit comment)
 
```

Was your pokemon predicted to be legendary (i.e. is the prediction close to 0 or 1)? Why or why not? Does it match character's Legendary status in dataset?

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 4: (2 pts)

We can measure how far off our predictions are from reality with residuals. Use `resid()` to find the residuals of each pokemon in the dataset then find the sum of all residuals. What is the sum of all the residuals. Why does it make sense? 

```{r}
# your code goes below (make sure to edit comment)
 
```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 5: (2 pts)

A logistic regression would be more appropriate to predict `Legendary` status since it can only take two values. Fit this new model with `Attack` and `HP`, call it `pokemon_log`, and write its equation. *Hint: the logit form is given by the R output.*

```{r}
# your code goes below (make sure to edit comment)
 
```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 6: (2 pts)

According to this new model, is the pokemon you chose in question 3 predicted to be legendary (i.e. probability is greater than 0.5)? Why or why not? 

*Hint: you can use predict() with the arguments `newdata =` and `type = "response"`.*

```{r}
# your code goes below (make sure to edit comment)
 
```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Question 7: (3 pts)

Let's compare the performance of these two models using ROC curves. On the same plot using `geom_roc()`, represent the ROC curve for predicting `Legendary` status based on the predictions from the linear regression in blue and another ROC curve based on the predictions from the logistic regression in orange.

*Hint: You will need to make predictions from both the `pokemon_lin` model object and the `pokemon_log` model object. For the `pokemon_log` model, make sure to make predictions using `type = "response"`.*

```{r}
# your code goes below (make sure to edit comment)
 
```

How do these two models compare?

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

## Formatting: (2 pts)

Comment your code, write full sentences, and knit your file!

------------------------------------------------------------------------

```{r, echo=F}
## DO NOT DELETE THIS BLOCK!
Sys.info()
```